The necessity of hypermedia RDF and an approach to achieve it

### 2012-04-12 eswc-2012/workshop2.tex
move CR into a new subsection
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@209 43ef1190-90fd-4dd7-a769-d0121f02b80e

We noted that for a read-write RESTful protocol, we need to say in the
RDF message itself what kind of operations can be made. We also note
that only information resources can be manipulated, and we argued that
it should be possible to add the required triples to every
resource. We should be able to define hypermedia RDF in terms of a
minimal vocabulary, but like the H~Factor web page, we will find it
instructive to use examples. In the following, we use Turtle syntax,
with prefixes omitted for brevity. Also, we note that in many cases,
we are making statements about the current resource, which given a
reasonable base URI can be written as \texttt{<>}. We have not found
the following factors to be relevant to RDF: \textsf{LE}, \textsf{CU}
and \textsf{LT} (though the latter may be supported by
RDForms\footnote{\url{http://vocab.deri.ie/rdforms}}?); and
\textsf{LO} and \textsf{CL} are trivially supported. The remaining are:

@@

\item[\textsf{CR}] Support for modifying control data for read requests
  (e.g. HTTP Accept-* headers).

\begin{verbatim}
<> hm:acceptsFormats <http://www.w3.org/ns/formats/Turtle> .
\end{verbatim}

@@

>>>>

We noted that for a read-write RESTful protocol, we need to say in the
RDF message itself what kind of operations can be made. We also note
that only information resources can be manipulated, and we argued that
it should be possible to add the required triples to every
resource. We should be able to define hypermedia RDF in terms of a
minimal vocabulary, but like the H~Factor web page, we will find it
instructive to use examples. In the following, we use Turtle syntax,
with prefixes omitted for brevity. Also, we note that in many cases,
we are making statements about the current resource, which given a
reasonable base URI can be written as \texttt{<>}. We have not found
the following factors to be relevant to RDF: \textsf{LE}, \textsf{CU},
\textsf{CR} and \textsf{LT} (though the latter may be supported by
RDForms\footnote{\url{http://vocab.deri.ie/rdforms}}?); and
\textsf{LO} and \textsf{CL} are trivially supported. The remaining
are:

@@

@@

\subsection{New H~Factors}

\begin{itemize}
\item Support for supplying control data relevant to subsequent requests.

\begin{verbatim}
<> hm:acceptsFormat <http://www.w3.org/ns/formats/Turtle> .
\end{verbatim}

\item Support for self-description.

\end{itemize}
